---
title: "Lab 02 - Plastic waste"
author: "Jonathan Trattner"
date: "Last compiled on `r format(Sys.time(), '%B %d, %Y')`"
output: 
  html_document:
    df_print: paged
    toc: true
    toc_depth: 4
    toc_float:
      collapsed: true
      smooth_scroll: true
    theme: journal
    highlight: monochrome
---

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

```{r load-data, message=FALSE}
plastic_waste <- read_csv("data/plastic-waste.csv")
```

## Exercises

### Exercise 1

The distributions are right-skewed! Maybe it looks like a $\gamma$ distribution.

```{r plastic-waste-continent}
ggplot(plastic_waste, aes(x = plastic_waste_per_cap)) +
  geom_histogram(binwidth = 0.2) + 
  facet_wrap(~continent)
```

### Exercise 2

Yep, definitely looks like a $\gamma$ distribution.

```{r plastic-waste-density}
ggplot(data = plastic_waste, aes(x = plastic_waste_per_cap)) +
  geom_density()
```

### Exercise 3

```{r plastic-waste-density-alpha}
ggplot(data = plastic_waste, 
       mapping = aes(x = plastic_waste_per_cap, 
                     color = continent, 
                     fill = continent)) +
  geom_density(alpha = 0.2)
```

We defined the color and fill of the curves by mapping the aesthetics of the plot because those are dependent upon the continent variable. We defined the alpha outside of that because that is independent of any variables. That is, we map aesthetics to variables but not things independent of them.

### Exercise 4

Remove this text, and add your answer for Exercise 4 here.

```{r plastic-waste-violin}
ggplot(data = plastic_waste, 
       mapping = aes(x = continent, 
                     y = plastic_waste_per_cap,
                     color = continent, 
                     fill = continent)) +
  geom_violin()
```

The violin plot reveals the relative distribution of each variable (i.e. the density within groupings). It is, according to the docs, a combination of `geom_density()` and `geom_boxplot()`.

### Exercise 5

Remove this text, and add your answer for Exercise 5 here.

```{r plastic-waste-mismanaged}
ggplot(data = plastic_waste, 
       mapping = aes(x = plastic_waste_per_cap, 
                     y = mismanaged_plastic_waste_per_cap)) +
  geom_point()
```

There seems to be a positive relationship between mismanaged plastic waste per cap and plastic waste per cap (perhaps unsurprisingly).

### Exercise 6 {#exercise-6}

Remove this text, and add your answer for Exercise 6 here.

```{r plastic-waste-mismanaged-continent}
ggplot(data = plastic_waste, 
       mapping = aes(x = plastic_waste_per_cap, 
                     y = mismanaged_plastic_waste_per_cap,
                     color = continent)) +
  geom_point()
```

There don't seem to be any *clear* distinctions between continents and plastic waste (mismanagement) per capita. Though *maybe* Asia and Africa look like they have a higher slope...?

### Exercise 7

Remove this text, and add your answer for Exercise 7 here.

```{r plastic-waste-population-total}
ggplot(data = plastic_waste, 
       mapping = aes(x = plastic_waste_per_cap, 
                     y = total_pop)) +
  geom_point()

```

```{r plastic-waste-population-coastal}
ggplot(data = plastic_waste, 
       mapping = aes(x = plastic_waste_per_cap, 
                     y = coastal_pop)) +
  geom_point()
```

Neither of these plots seem to have a stronger linear relationship than the one seen in [exercise 6](#exercise-6)

### Exercise 8

Remove this text, and add your answer for Exercise 8 here.

```{r recreate-viz}

plastic_waste %>%
  mutate(coast_prop = coastal_pop / total_pop) %>%
  filter(plastic_waste_per_cap < 3) %>%
  ggplot(aes(x = coast_prop,
             y = plastic_waste_per_cap)) +
  geom_point(aes(color = continent)) +
  geom_smooth(color = "black") +
  scale_color_viridis_d() +
  theme_minimal() +
  labs(title = "Plastic waste vs. coastal population proportion",
       subtitle = "by continent",
       color = "Continent",
       x = "Coastal population proportion (Coastal / total population)",
       y = "Plastic waste per capita")
```
