---
title: "Lab 02 - Plastic waste"
author: "Jonathan Trattner"
date: "Last compiled on `r format(Sys.time(), '%B %d, %Y')`"
output: 
  html_document:
    df_print: paged
    toc: true
    toc_depth: 4
    toc_float:
      collapsed: true
      smooth_scroll: true
    theme: journal
    highlight: monochrome
---

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

```{r load-data, message=FALSE}
plastic_waste <- read_csv("data/plastic-waste.csv")
```

## Exercises

### Exercise 1

The distributions are right-skewed! Maybe it looks like a $\gamma$ distribution.

```{r plastic-waste-continent}
ggplot(plastic_waste, aes(x = plastic_waste_per_cap)) +
  geom_histogram(binwidth = 0.2) + 
  facet_wrap(~continent)
```

### Exercise 2

```{r plastic-waste-density}
# insert code here
```

### Exercise 3

Remove this text, and add your answer for Exercise 3 here.

### Exercise 4

Remove this text, and add your answer for Exercise 4 here.

```{r plastic-waste-violin}
# insert code here
```

### Exercise 5

Remove this text, and add your answer for Exercise 5 here.

```{r plastic-waste-mismanaged}
# insert code here
```

### Exercise 6

Remove this text, and add your answer for Exercise 6 here.

```{r plastic-waste-mismanaged-continent}
# insert code here
```

### Exercise 7

Remove this text, and add your answer for Exercise 7 here.

```{r plastic-waste-population-total}
# insert code here
```

```{r plastic-waste-population-coastal}
# insert code here
```

### Exercise 8

Remove this text, and add your answer for Exercise 8 here.

```{r recreate-viz}
# insert code here
```
