---
title: "Lab 02 - Plastic waste"
author: "Jonathan Trattner"
date: "Last compiled on `r format(Sys.time(), '%B %d, %Y')`"
output: 
  html_document:
    df_print: paged
    toc: true
    toc_depth: 4
    toc_float:
      collapsed: true
      smooth_scroll: true
    theme: journal
    highlight: monochrome
---

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

```{r load-data, message=FALSE}
plastic_waste <- read_csv("data/plastic-waste.csv")
```

## Exercises

### Exercise 1

The distributions are right-skewed! Maybe it looks like a $\gamma$ distribution.

```{r plastic-waste-continent}
ggplot(plastic_waste, aes(x = plastic_waste_per_cap)) +
  geom_histogram(binwidth = 0.2) + 
  facet_wrap(~continent)
```

### Exercise 2

Yep, definitely looks like a $\gamma$ distribution.

```{r plastic-waste-density}
ggplot(data = plastic_waste, aes(x = plastic_waste_per_cap)) +
  geom_density()
```

### Exercise 3

```{r plastic-waste-density-alpha}
ggplot(data = plastic_waste, 
       mapping = aes(x = plastic_waste_per_cap, 
                     color = continent, 
                     fill = continent)) +
  geom_density(alpha = 0.2)
```

We defined the color and fill of the curves by mapping the aesthetics of the plot because those are dependent upon the continent variable. We defined the alpha outside of that because that is independent of any variables. That is, we map aesthetics to variables but not things independent of them.

### Exercise 4

Remove this text, and add your answer for Exercise 4 here.

```{r plastic-waste-violin}
ggplot(data = plastic_waste, 
       mapping = aes(x = continent, 
                     y = plastic_waste_per_cap,
                     color = continent, 
                     fill = continent)) +
  geom_violin()
```

The violin plot reveals the relative distribution of each variable (i.e. the density within groupings). It is, according to the docs, a combination of `geom_density()` and `geom_boxplot()`.

### Exercise 5

Remove this text, and add your answer for Exercise 5 here.

```{r plastic-waste-mismanaged}
# insert code here
```

### Exercise 6

Remove this text, and add your answer for Exercise 6 here.

```{r plastic-waste-mismanaged-continent}
# insert code here
```

### Exercise 7

Remove this text, and add your answer for Exercise 7 here.

```{r plastic-waste-population-total}
# insert code here
```

```{r plastic-waste-population-coastal}
# insert code here
```

### Exercise 8

Remove this text, and add your answer for Exercise 8 here.

```{r recreate-viz}
# insert code here
```
